Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''

### 2019-05-22 tex/v3/section_4_marginal_viols.tex
update

\end{proposition}
Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma 1 in supplementary).
Note that $c_\kappa$ and $c_{\frac 1\kappa}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.

>>>>

\end{proposition}
Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma~\ref{lem:pinsker} in supplementary).
Note that $c_\kappa$ and $c_{\frac 1\kappa}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.
